Tree-based Methods

### 2025-07-20 papers.qmd
Update website content and navigation structure
Renamed the 'Code' section to 'Software' in _quarto.yml for clarity. Enhanced the 'About' page with a more detailed overview of Professor Bin Yu's achievements and research focus, while streamlining the content for better readability. Removed the 'code.qmd' file to consolidate software information into the new 'Software' section. Updated the index.qmd layout to improve the presentation of recent publications and news.

Q. Wang*, T. M. Tang*, N. Youlton, C. S. Weldy, A. M. Kenney, O. Ronen, J. W. Hughes, E. T. Chin, S. C. Sutton, A. Agarwal, X. Li, M. Behr, K. Kumbier, C. S. Moravec, W. H. W. Tang, K. B. Margulies, T. P. Cappola, A. J. Buitte, R. Arnaout, J. B. Brown, J. R. Priest, V. N. Parikh, B. Yu*, E. Ashley* (2023). Epistasis regulates genetic control of cardiac hypertrophy. [medRxiv](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) ([Code](https://github.com/Yu-Group/epistasis-cardiac-hypertrophy)) ([PCS documentation](https://yu-group.github.io/epistasis-cardiac-hypertrophy/#overview))

R. Cahill, Y. Wang, R. P. Xian, A. J. Lee, H. Zeng, B. Yu, B. Tasic, R. Abbasi-Asl (2023). Unsupervised pattern discovery in spatial gene expression atlas reveals mouse brain regions beyond established ontology. [bioRxiv](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2) ([Code](https://github.com/abbasilab/osNMF))

@@

K. Wu, Y. Chen, W. Ha, B. Yu (2023). [Prominent roles of conditionally invariant components in domain adaptation: theory and algorithms.](https://arxiv.org/abs/2309.10301) JMLR (accepted). [https://arxiv.org/abs/2309.10301](https://arxiv.org/abs/2309.10301)

N. Ghosh, S. Frei, W. Ha, B. Yu (2023). The effect of SGD batch size on autoencoder learning: sparsity, sharpness and feature learning. [https://arxiv.org/abs/2308.03215](https://arxiv.org/abs/2308.03215)

R. Netzorg, J. Li, B. Yu (2024). Improving prototypical part networks with reward reweighting, reselection, and retraining. Proc. ICML. [https://arxiv.org/abs/2307.03887](https://arxiv.org/abs/2307.03887)

A. Agarwal, A. M. Kenny, Y. S. Tan, T. M. Tang, B. Yu (2023). MDI+: a flexible random forest-based feature importance framework. [https://arxiv.org/abs/2307.01932](https://arxiv.org/abs/2307.01932) (PCS related)

A. R. Hsu, Y. Cherapanamjeri, B. Park, T. Naumann, A. Odisho, and B. Yu (2023). Diagnosing transformers: illuminating feature space for clinical decison-making. Proc. ICLR. [https://arxiv.org/abs/2305.17588](https://arxiv.org/abs/2305.17588)

C. Singh, A. R. Hsu, R. Antonello, S. Jain, A. G. Huth, B. Yu and J. Gao (2023). Explaining black box text modules in natural language with language models. [https://arxiv.org/abs/2305.09863](https://arxiv.org/abs/2305.09863)

@@

D. Shen, P. Ding, J. Sekhon, B. Yu (2022). Same root different leaves: time series and cross-sectional methods in panel data. Econometrica (accepted). [https://arxiv.org/abs/2207.14481](https://arxiv.org/abs/2207.14481)

@@

N. Altieri, B. Park, M. Olson, J. DeNero, A. Odisho, B. Yu. (2021). Supervised line attention for tumor attribute classification from pathology reports: Higher performance with less data. Journal of Biomedical Informatics. 122 (2021) 103872. [arXiv version](https://arxiv.org/abs/2012.08113)

@@

M. Behr*, K. Kumbier*, A. Cordova-Palomera, M. Aguirre, E. Ashley, A. Butte, R. Arnaout, J. B. Brown, J. Preist*, B. Yu* (2020). [Learning epistatic polygenic phenotypes with Boolean interactions](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) ([code](https://github.com/merlebehr/epiTree)) (PCS inference case study)

@@

X. Li, T. M. Tang, X. Wang, J. A. Kocher, B. Yu (2020). [A stability-driven protocol for drug response interpretable prediction (staDRIP)](https://arxiv.org/abs/2011.06593). NeurISP workshop on ML4H (Machine learning for Health) Extended Abstract.

@@

N. Altieri, R. Barter, J. Duncan, R. Dwivedi, K. Kumbier, X. Li, R. Netzorg, B. Park, C. Singh*, Y. Tan, T.Tang, Y. Wang, C. Zhang, B. Yu*. (2020) [Curating a COVID-19 data repository and forecasting county-level death counts in the United States.](https://hdsr.mitpress.mit.edu/pub/p6isyf0g/release/1) Harvard Data Science Review ([code](https://github.com/Yu-Group/covid19-severity-prediction)) [7-day prediction results](https://covidseverity.com/) [Short talk video](https://www.stat.berkeley.edu/~binyu/ps/papers2020/RDSS20-yu.mp4)

B. Yu and K. Kumbier (2020) [Veridical data science](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-YuKumbier.pdf) (PCS framework), PNAS. 117 (8), 3920-3929. [QnAs with Bin Yu.](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-QnAsBinYu.pdf)

@@

Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2020) [Fast Mixing of Metropolized Hamiltonian Monte Carlo: Benefits of Multi-Step Gradients,](https://www.jmlr.org/papers/volume21/19-441/19-441.pdf) JMLR, [arXiv](https://arxiv.org/abs/1905.12247)

@@

Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2018) [Fast MCMC Algorithms on Polytopes](http://jmlr.org/papers/v19/18-158.html). JMLR . http://jmlr.org/papers/v19/18-158.html

Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2020) [Vaidya Walk: A Sampling Algorithm Based on Volumetric-Logarithmic Barrier](https://ieeexplore.ieee.org/abstract/document/8262876/) Allerton Conference 2017 https://ieeexplore.ieee.org/abstract/document/8262876/

@@

Y. Wang, S. Wu and B. Yu (2020) [Unique Sharp Local Minimum in l1-minimization Complete Dictionary Learning.](https://jmlr.org/papers/volume21/19-169/19-169.pdf) JMLR. 21(63), pp. 1-52. Also at https://arxiv.org/abs/1902.08380

Y. Chen, R. Abbasi-Asl, A. Bloniarz, M. Oliver, B. Willmore, J. Gallant*, and B. Yu* (2018) [The DeepTune framework for modeling and characterizing neurons in visual cortex area V4](https://www.biorxiv.org/content/10.1101/465534v1) https://www.biorxiv.org/content/10.1101/465534v1

K. Kumbier, S. Sumanta, J. B. Brown, S. Celniker, and B. Yu* (2018) [Refining interaction search through signed iterative Random Forests.](https://arxiv.org/abs/1810.07287) [https://arxiv.org/abs/1810.0728](https://arxiv.org/abs/1810.0728) (an enhanced version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS related)

@@

J. Murdoch, P. Liu, and B. Yu (2018) [Beyond word importance: contextual decomposition to extract interactions from LSTMs.](https://arxiv.org/abs/1801.05453) Proc. ICLR 2018. [https://arxiv.org/abs/1705.07356](https://arxiv.org/abs/1705.07356) ([code)](https://github.com/csinva/hierarchical-dnn-interpretations)

R. Diwivedi, Y. Chen, M. J. Wainwright, and B. Yu (2018) [Log-concave sampling: Metropolis-Hastings algorithms are fast!](https://arxiv.org/abs/1801.02309) https://arxiv.org/abs/1801.02309.

@@

Y. Chen, R. Dwivedi, M. J. Wainwright, and B. Yu (2017) [Fast MCMC sampling algorithms on polytopes](https://arxiv.org/abs/1710.08165) https://arxiv.org/abs/1710.08165.

@@

R. Abbasi-Asl and B. Yu (2017) [Structural Compression of Convolutional Neural Networks Based on Greedy Filter Pruning](https://arxiv.org/abs/1705.07356) https://arxiv.org/abs/1705.07356

R. Abbasi-Asl and B. Yu (2017) [Interpreting Convolutional Neural Networks Through Compression.](https://arxiv.org/abs/1711.02329) NIPS 2017. Symposium on Interpretable Machine Learning. (also https://arxiv.org/abs/1711.02329)

S. Kunzel, J. Sekhon, P. Bickel, and B. Yu* (2019) [Meta-learners for Estimating Heterogeneous Treatment Effects using Machine Learning,](https://www.pnas.org/content/116/10/4156) PNAS. 116 (10) 4156-4165.  https://arxiv.org/abs/1706.03461. [(code](https://github.com/soerenkuenzel/hte))

>>>>

Q. Wang*, T. M. Tang*, N. Youlton, C. S. Weldy, A. M. Kenney, O. Ronen, J. W. Hughes, E. T. Chin, S. C. Sutton, A. Agarwal, X. Li, M. Behr, K. Kumbier, C. S. Moravec, W. H. W. Tang, K. B. Margulies, T. P. Cappola, A. J. Buitte, R. Arnaout, J. B. Brown, J. R. Priest, V. N. Parikh, B. Yu*, E. Ashley* (2023). [Epistasis regulates genetic control of cardiac hypertrophy.](https://www.medrxiv.org/content/10.1101/2023.11.06.23297858v1) ([Code](https://github.com/Yu-Group/epistasis-cardiac-hypertrophy)) ([PCS documentation](https://yu-group.github.io/epistasis-cardiac-hypertrophy/#overview))

R. Cahill, Y. Wang, R. P. Xian, A. J. Lee, H. Zeng, B. Yu, B. Tasic, R. Abbasi-Asl (2023). [Unsupervised pattern discovery in spatial gene expression atlas reveals mouse brain regions beyond established ontology.](https://www.biorxiv.org/content/10.1101/2023.03.10.531984v2) ([Code](https://github.com/abbasilab/osNMF))

@@

K. Wu, Y. Chen, W. Ha, B. Yu (2023). [Prominent roles of conditionally invariant components in domain adaptation: theory and algorithms.](https://arxiv.org/abs/2309.10301) JMLR (accepted).

N. Ghosh, S. Frei, W. Ha, B. Yu (2023). [The effect of SGD batch size on autoencoder learning: sparsity, sharpness and feature learning.](https://arxiv.org/abs/2308.03215)

R. Netzorg, J. Li, B. Yu (2024). [Improving prototypical part networks with reward reweighting, reselection, and retraining.](https://arxiv.org/abs/2307.03887) Proc. ICML.

A. Agarwal, A. M. Kenny, Y. S. Tan, T. M. Tang, B. Yu (2023). [MDI+: a flexible random forest-based feature importance framework.](https://arxiv.org/abs/2307.01932) (PCS related)

A. R. Hsu, Y. Cherapanamjeri, B. Park, T. Naumann, A. Odisho, and B. Yu (2023). [Diagnosing transformers: illuminating feature space for clinical decison-making.](https://arxiv.org/abs/2305.17588) Proc. ICLR.

C. Singh, A. R. Hsu, R. Antonello, S. Jain, A. G. Huth, B. Yu and J. Gao (2023). [Explaining black box text modules in natural language with language models.](https://arxiv.org/abs/2305.09863)

@@

D. Shen, P. Ding, J. Sekhon, B. Yu (2022). [Same root different leaves: time series and cross-sectional methods in panel data.](https://arxiv.org/abs/2207.14481) Econometrica (accepted).

@@

N. Altieri, B. Park, M. Olson, J. DeNero, A. Odisho, B. Yu. (2021). [Supervised line attention for tumor attribute classification from pathology reports: Higher performance with less data.](https://arxiv.org/abs/2012.08113) Journal of Biomedical Informatics. 122 (2021) 103872.

@@

M. Behr*, K. Kumbier*, A. Cordova-Palomera, M. Aguirre, E. Ashley, A. Butte, R. Arnaout, J. B. Brown, J. Preist*, B. Yu* (2020). [Learning epistatic polygenic phenotypes with Boolean interactions.](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) ([code](https://github.com/merlebehr/epiTree)) (PCS inference case study)

@@

X. Li, T. M. Tang, X. Wang, J. A. Kocher, B. Yu (2020). [A stability-driven protocol for drug response interpretable prediction (staDRIP).](https://arxiv.org/abs/2011.06593) NeurISP workshop on ML4H (Machine learning for Health) Extended Abstract.

@@

N. Altieri, R. Barter, J. Duncan, R. Dwivedi, K. Kumbier, X. Li, R. Netzorg, B. Park, C. Singh*, Y. Tan, T.Tang, Y. Wang, C. Zhang, B. Yu*. (2020) [Curating a COVID-19 data repository and forecasting county-level death counts in the United States.](https://hdsr.mitpress.mit.edu/pub/p6isyf0g/release/1) Harvard Data Science Review ([code](https://github.com/Yu-Group/covid19-severity-prediction)) ([7-day prediction results](https://covidseverity.com/)) ([Short talk video](https://www.stat.berkeley.edu/~binyu/ps/papers2020/RDSS20-yu.mp4))

B. Yu and K. Kumbier (2020) [Veridical data science](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-YuKumbier.pdf) (PCS framework), PNAS. 117 (8), 3920-3929. ([QnAs with Bin Yu](https://www.stat.berkeley.edu/~binyu/ps/papers2020/VDS20-QnAsBinYu.pdf))

@@

Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2020) [Fast Mixing of Metropolized Hamiltonian Monte Carlo: Benefits of Multi-Step Gradients.](https://www.jmlr.org/papers/volume21/19-441/19-441.pdf) JMLR, ([arXiv](https://arxiv.org/abs/1905.12247))

@@

Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2018) [Fast MCMC Algorithms on Polytopes.](http://jmlr.org/papers/v19/18-158.html) JMLR.

Y. Chen, R. Dwivedi, M. J. Wainwright and B. Yu (2020) [Vaidya Walk: A Sampling Algorithm Based on Volumetric-Logarithmic Barrier.](https://ieeexplore.ieee.org/abstract/document/8262876/) Allerton Conference 2017.

@@

Y. Wang, S. Wu and B. Yu (2020) [Unique Sharp Local Minimum in l1-minimization Complete Dictionary Learning.](https://jmlr.org/papers/volume21/19-169/19-169.pdf) JMLR. 21(63), pp. 1-52. ([arXiv](https://arxiv.org/abs/1902.08380))

Y. Chen, R. Abbasi-Asl, A. Bloniarz, M. Oliver, B. Willmore, J. Gallant*, and B. Yu* (2018) [The DeepTune framework for modeling and characterizing neurons in visual cortex area V4.](https://www.biorxiv.org/content/10.1101/465534v1)

K. Kumbier, S. Sumanta, J. B. Brown, S. Celniker, and B. Yu* (2018) [Refining interaction search through signed iterative Random Forests.](https://arxiv.org/abs/1810.07287) (an enhanced version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS related)

@@

J. Murdoch, P. Liu, and B. Yu (2018) [Beyond word importance: contextual decomposition to extract interactions from LSTMs.](https://arxiv.org/abs/1801.05453) Proc. ICLR 2018. ([code](https://github.com/csinva/hierarchical-dnn-interpretations))

R. Diwivedi, Y. Chen, M. J. Wainwright, and B. Yu (2018) [Log-concave sampling: Metropolis-Hastings algorithms are fast!](https://arxiv.org/abs/1801.02309)

@@

Y. Chen, R. Dwivedi, M. J. Wainwright, and B. Yu (2017) [Fast MCMC sampling algorithms on polytopes.](https://arxiv.org/abs/1710.08165)

@@

R. Abbasi-Asl and B. Yu (2017) [Structural Compression of Convolutional Neural Networks Based on Greedy Filter Pruning.](https://arxiv.org/abs/1705.07356)

R. Abbasi-Asl and B. Yu (2017) [Interpreting Convolutional Neural Networks Through Compression.](https://arxiv.org/abs/1711.02329) NIPS 2017. Symposium on Interpretable Machine Learning.

S. Kunzel, J. Sekhon, P. Bickel, and B. Yu* (2019) [Meta-learners for Estimating Heterogeneous Treatment Effects using Machine Learning.](https://www.pnas.org/content/116/10/4156) PNAS. 116 (10) 4156-4165. ([arXiv](https://arxiv.org/abs/1706.03461)) ([code](https://github.com/soerenkuenzel/hte))

### 2025-07-20 papers/interpretable-machine-learning.qmd
Update website content and navigation structure
Renamed the 'Code' section to 'Software' in _quarto.yml for clarity. Enhanced the 'About' page with a more detailed overview of Professor Bin Yu's achievements and research focus, while streamlining the content for better readability. Removed the 'code.qmd' file to consolidate software information into the new 'Software' section. Updated the index.qmd layout to improve the presentation of recent publications and news.

1. A. R. Hsu, Y. Cherapanamjeri, A. Y. Odisho, P. R. Carroll, B. Yu (2024). [Mechanistic Interpretation through Contexual Decomposition in Transformers.](https://arxiv.org/pdf/2407.00886) [https://arxiv.org/pdf/2407.00886](https://arxiv.org/pdf/2407.00886).
1. Y. Chen, C. Singh, X. Liu, S. Zuo, B. Yu, H. He, J. Gao (2024). [Towards consistent natural-language explanations via explanation-consistent finetuning.](https://arxiv.org/abs/2401.13986) [https://arxiv.org/abs/2401.13986](https://arxiv.org/abs/2401.13986)
1. Q. Zhang, C. Singh, L. Liu, X. Liu, B. Yu, J. Gao, T. Zhao (2023). [Tell your model where to attend: post-hoc attention steering for LLMs.](https://arxiv.org/abs/2311.02262) ICLR 2024. https://arxiv.org/abs/2311.02262
1. A. Agarwal, A. M. Kenny, Y. S. Tan, T. M. Tang, B. Yu (2023). MDI+: a flexible random forest-based feature importance framework. [https://arxiv.org/abs/2307.01932](https://arxiv.org/abs/2307.01932) (PCS related)
1. A. R. Hsu, Y. Cherapanamjeri, B. Park, T. Naumann, A. Odisho, and B. Yu (2023). [Diagnosing transformers: illuminating feature space for clinical decison-making.](https://arxiv.org/abs/2305.17588) ICLR (2024) [https://arxiv.org/abs/2305.17588](https://arxiv.org/abs/2305.17588)
1. C. Singh, A. R. Hsu, R. Antonello, S. Jain, A. G. Huth, B. Yu and J. Gao (2023). [Explaining black box text modules in natural language with language models.](https://arxiv.org/abs/2305.09863)
1. C. Singh, W. Ha and B. Yu (2021). [Interpreting and Improving Deep-Learning Models with Reality Checks](https://arxiv.org/abs/2108.06847). [https://arxiv.org/abs/2108.06847](https://arxiv.org/abs/2108.06847) to appear in the book entitled "xxAI - Beyond Explainable AI" (eds. Andreas Holzinger, Randy Goebel, Ruth Fong, Taesup Moon, Klaus-Robert Müller, and Wojciech Samek).
1. W. Ha, C. Singh, F. Lanusse, S. Upadhyayula, and B. Yu (2021). [Adaptive Wavelet Distillation from Neural Networks through Interpretation.](https://nips.cc/Conferences/2021/ScheduleMultitrack?event=28027) Proc. NeurIPS 2021. ([code](https://github.com/Yu-Group/adaptive-wavelets))
1. L. Reiger, J. W. Murdoch, S. Singh, B. Yu (2020). [Interpretations are Useful: Penalizing Explanations to Align Neural Networks with Prior Knowledge](https://proceedings.icml.cc/static/paper_files/icml/2020/992-Paper.pdf). ICML Proceedings. ([code](https://github.com/laura-rieger/deep-explanation-penalization))
1. C. Singh, W. Ha, F. Lanusse, V. Boehm , J. Liu, B. Yu (2020). [Transformation Importance with Applications to Cosmology](https://arxiv.org/pdf/2003.01926.pdf) ICLR Workshop paper. ([code](https://github.com/csinva/transformation-importance))
1. W. J. Murdoch, C. Singh, K. Kumbier, R. Abbasi-Asl, and B. Yu* (2019) [Definitions, methods, and applications in interpretable machine learning.](https://www.stat.berkeley.edu/~binyu/ps/papers2020/iML19-Murdochetal.pdf) PNAS, 116 (44) 22071-22080.
1. W. J. Murdoch, C. Sign, and B. Yu (2019). [Hierarchical interpretations for neural network predictions.](https://openreview.net/pdf?id=SkEqro0ctQ) ICLR. ([code](https://github.com/csinva/hierarchical-dnn-interpretations))
1. J. Murdoch, P. Liu, and B. Yu (2018) [Beyond word importance: contextual decomposition to extract interactions from LSTMs.](https://arxiv.org/abs/1801.05453) Proc. ICLR 2018. [https://arxiv.org/abs/1705.07356](https://arxiv.org/abs/1705.07356) ([code](https://github.com/csinva/hierarchical-dnn-interpretations))

>>>>

1. A. R. Hsu, Y. Cherapanamjeri, A. Y. Odisho, P. R. Carroll, B. Yu (2024). [Mechanistic Interpretation through Contextual Decomposition in Transformers.](https://arxiv.org/pdf/2407.00886)
1. Y. Chen, C. Singh, X. Liu, S. Zuo, B. Yu, H. He, J. Gao (2024). [Towards consistent natural-language explanations via explanation-consistent finetuning.](https://arxiv.org/abs/2401.13986)
1. Q. Zhang, C. Singh, L. Liu, X. Liu, B. Yu, J. Gao, T. Zhao (2023). [Tell your model where to attend: post-hoc attention steering for LLMs.](https://arxiv.org/abs/2311.02262) ICLR 2024.
1. A. Agarwal, A. M. Kenny, Y. S. Tan, T. M. Tang, B. Yu (2023). [MDI+: a flexible random forest-based feature importance framework.](https://arxiv.org/abs/2307.01932) (PCS related)
1. A. R. Hsu, Y. Cherapanamjeri, B. Park, T. Naumann, A. Odisho, and B. Yu (2023). [Diagnosing transformers: illuminating feature space for clinical decision-making.](https://arxiv.org/abs/2305.17588) ICLR (2024)
1. C. Singh, A. R. Hsu, R. Antonello, S. Jain, A. G. Huth, B. Yu and J. Gao (2023). [Explaining black box text modules in natural language with language models.](https://arxiv.org/abs/2305.09863)
1. C. Singh, W. Ha and B. Yu (2021). [Interpreting and Improving Deep-Learning Models with Reality Checks.](https://arxiv.org/abs/2108.06847) To appear in the book entitled "xxAI - Beyond Explainable AI" (eds. Andreas Holzinger, Randy Goebel, Ruth Fong, Taesup Moon, Klaus-Robert Müller, and Wojciech Samek).
1. W. Ha, C. Singh, F. Lanusse, S. Upadhyayula, and B. Yu (2021). [Adaptive Wavelet Distillation from Neural Networks through Interpretation.](https://nips.cc/Conferences/2021/ScheduleMultitrack?event=28027) Proc. NeurIPS 2021. ([code](https://github.com/Yu-Group/adaptive-wavelets))
1. L. Reiger, J. W. Murdoch, S. Singh, B. Yu (2020). [Interpretations are Useful: Penalizing Explanations to Align Neural Networks with Prior Knowledge](https://proceedings.icml.cc/static/paper_files/icml/2020/992-Paper.pdf). ICML Proceedings. ([code](https://github.com/laura-rieger/deep-explanation-penalization))
1. C. Singh, W. Ha, F. Lanusse, V. Boehm , J. Liu, B. Yu (2020). [Transformation Importance with Applications to Cosmology](https://arxiv.org/pdf/2003.01926.pdf) ICLR Workshop paper. ([code](https://github.com/csinva/transformation-importance))
1. W. J. Murdoch, C. Singh, K. Kumbier, R. Abbasi-Asl, and B. Yu* (2019) [Definitions, methods, and applications in interpretable machine learning.](https://www.stat.berkeley.edu/~binyu/ps/papers2020/iML19-Murdochetal.pdf) PNAS, 116 (44) 22071-22080.
1. W. J. Murdoch, C. Sign, and B. Yu (2019). [Hierarchical interpretations for neural network predictions.](https://openreview.net/pdf?id=SkEqro0ctQ) ICLR. ([code](https://github.com/csinva/hierarchical-dnn-interpretations))
1. J. Murdoch, P. Liu, and B. Yu (2018) [Beyond word importance: contextual decomposition to extract interactions from LSTMs.](https://arxiv.org/abs/1801.05453) Proc. ICLR 2018. ([code](https://github.com/csinva/hierarchical-dnn-interpretations))

### 2025-07-20 papers/tree-based-methods.qmd
Update website content and navigation structure
Renamed the 'Code' section to 'Software' in _quarto.yml for clarity. Enhanced the 'About' page with a more detailed overview of Professor Bin Yu's achievements and research focus, while streamlining the content for better readability. Removed the 'code.qmd' file to consolidate software information into the new 'Software' section. Updated the index.qmd layout to improve the presentation of recent publications and news.

1. Y. S. Tan, O. Ronen, T. Saarinen, B. Yu (2024). [The Computational Curse of Big Data for Bayesian Additive Regression Trees: a Hitting Time Analysis.](https://arxiv.org/pdf/2406.19958) [https://arxiv.org/pdf/2406.19958](https://arxiv.org/pdf/2406.19958).
1. Y. S. Tan, C. Singh, K. Nasseri, A. Agarwal, J. Duncan, O. Ronen, M. Epland, A. Kornblith, B. Yu (2022). [Fast interpretable greedy-tree sums (FIGS)](https://arxiv.org/abs/2201.11931). https://arxiv.org/abs/2201.11931 ([imodels 🔎: a python package for fitting interpretable models](https://github.com/csinva/imodels) contains code for FIGS).
1. M. Behr, Y. Wang, X. Li, B. Yu (2022). [Provable Boolean Interaction Recovery from Tree Ensemble obtained via Random Forests.](https://arxiv.org/abs/2102.11800) PNAS, [https://arxiv.org/abs/2102.11800](https://arxiv.org/abs/2102.11800) (theory for a tractable version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS-related)
1. A. Agarwal, Y. S. Tan, O. Ronen, C. Singh, B. Yu (2022). [Hierarchical shrinkage: improving accuracy and interpretability of tree-based methods.](https://arxiv.org/abs/2202.00858) Proc. ICML [https://arxiv.org/abs/2202.00858](https://arxiv.org/abs/2202.00858) ([imodels 🔎: a python package for fitting interpretable models](https://github.com/csinva/imodels) contains code for hierarchical shrinkage (HS))
1. Y. Tan, A. Agarwal, and B. Yu (2021). [A cautionary tale on fitting decision trees to data from additive models: generalization lower bounds.](https://arxiv.org/abs/2110.09626) Proc. AISTATS, [https://arxiv.org/abs/2110.09626](https://arxiv.org/abs/2110.09626)
1. M. Behr*, K. Kumbier*, A. Cordova-Palomera, M. Aguirre, E. Ashley, A. Butte, R. Arnaout, J. B. Brown, J. Preist*, B. Yu* (2020). [Learning epistatic polygenic phenotypes with Boolean interactions](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) [https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) ([code](https://github.com/merlebehr/epiTree)) (PCS inference case study)
1. K. Kumbier, S. Sumanta, J. B. Brown, S. Celniker, and B. Yu* (2018) [Refining interaction search through signed iterative Random Forests.](https://arxiv.org/abs/1810.07287) [https://arxiv.org/abs/1810.0728](https://arxiv.org/abs/1810.0728) (an enhanced version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS related)
1. S. Basu, K. Kumbier, J. B. Brown*, and B. Yu* (2018) [iterative Random Forests to discover predictive and stable high-order interactions](https://www.stat.berkeley.edu/~binyu/ps/papers2018/iRF+SI18.pdf) PNAS, 115 (8), 1943-1948. ([code](https://github.com/Yu-Group/iterative-Random-Forest)) (PCS related)

>>>>

1. Y. S. Tan, O. Ronen, T. Saarinen, B. Yu (2024). [The Computational Curse of Big Data for Bayesian Additive Regression Trees: a Hitting Time Analysis.](https://arxiv.org/pdf/2406.19958)
1. Y. S. Tan, C. Singh, K. Nasseri, A. Agarwal, J. Duncan, O. Ronen, M. Epland, A. Kornblith, B. Yu (2022). [Fast interpretable greedy-tree sums (FIGS).](https://arxiv.org/abs/2201.11931) ([imodels 🔎: a python package for fitting interpretable models](https://github.com/csinva/imodels) contains code for FIGS).
1. M. Behr, Y. Wang, X. Li, B. Yu (2022). [Provable Boolean Interaction Recovery from Tree Ensemble obtained via Random Forests.](https://arxiv.org/abs/2102.11800) PNAS, (theory for a tractable version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS-related)
1. A. Agarwal, Y. S. Tan, O. Ronen, C. Singh, B. Yu (2022). [Hierarchical shrinkage: improving accuracy and interpretability of tree-based methods.](https://arxiv.org/abs/2202.00858) Proc. ICML ([imodels 🔎: a python package for fitting interpretable models](https://github.com/csinva/imodels) contains code for hierarchical shrinkage (HS))
1. Y. Tan, A. Agarwal, and B. Yu (2021). [A cautionary tale on fitting decision trees to data from additive models: generalization lower bounds.](https://arxiv.org/abs/2110.09626) Proc. AISTATS.
1. M. Behr*, K. Kumbier*, A. Cordova-Palomera, M. Aguirre, E. Ashley, A. Butte, R. Arnaout, J. B. Brown, J. Preist*, B. Yu* (2020). [Learning epistatic polygenic phenotypes with Boolean interactions.](https://www.biorxiv.org/content/10.1101/2020.11.24.396846v1) ([code](https://github.com/merlebehr/epiTree)) (PCS inference case study)
1. K. Kumbier, S. Sumanta, J. B. Brown, S. Celniker, and B. Yu* (2018) [Refining interaction search through signed iterative Random Forests.](https://arxiv.org/abs/1810.07287) (an enhanced version of [iRF](https://www.pnas.org/doi/10.1073/pnas.1711236115), PCS related)
1. S. Basu, K. Kumbier, J. B. Brown*, and B. Yu* (2018) [iterative Random Forests to discover predictive and stable high-order interactions](https://www.stat.berkeley.edu/~binyu/ps/papers2018/iRF+SI18.pdf) PNAS, 115 (8), 1943-1948. ([code](https://github.com/Yu-Group/iterative-Random-Forest)) (PCS related)
